---
title: "Schwartz et al., 1987"
output: html_notebook
editor_options: 
  markdown: 
    wrap: 72
---

# Effect size

## Gathering information:

Participants: 1) Schizophrenia n = 19

2)  Control n = 15

Contrast sensitivity (p6) 1) Main effect of groups for Pattern detection
(0Hz) F(1,32) = 1.77 , p = 0.2

2)  Main effects of SF (not significant for any SF) F(1,32) = 2.51 , p =
    0.12

3)  Interaction SF x groups (not significant) F(2,64) = 0.94 , p = 1.397

## Calculate effect size:

use the F-statistic (see bookdown.org)

### Main effects of group (2 groups)

F(1,32) = 1.77 , p = 0.2

```{r}
schwartz_1987_es_f <- esc_f(f = 1.77,      # F value of the one-way anova
      grp1n = 19,   # sample size of group 1 
      grp2n = 15,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD
schwartz_1987_es_f
```

### Main effects of SF (not significant for any SF) (2 groups)

F(1,32) = 2.51 , p = 0.12

```{r}
schwartz_1987_es_f_sf <- esc_f(f = 2.51,      # F value of the one-way anova
      grp1n = 19,   # sample size of group 1 
      grp2n = 15,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD
schwartz_1987_es_f_sf
```

## Scrapping data from Figure 2

### Scrapping 0.8 Hz - other Hz is not important for us.

Control (n=15) SF = 0.9, mean = 76.40378395835765, SEM-interval =
71.98737669712817 (lower limit) SF = 3.8, Not in graph SF = 15 , mean =
67.35015261075841, SEM-interval = 63.1545722830155 (lower limit)

Schizophrenia (n=19) SF = 0.9, mean = 80.15773063582003, SEM-interval =
85.67823213109716 (upper limit) SF = 3.8, Not in graph SF = 15 , mean =
49.24290002390624, SEM-interval = 53.659307285135725 -
45.709780279930435

### Calculate es from SF = 0.9

Control (n=15) SF = 0.9, mean = 76.40378395835765, SEM-interval =
71.98737669712817 (lower limit) Schizophrenia (n=19) SF = 0.9, mean =
80.15773063582003, SEM-interval = 85.67823213109716 (upper limit)

```{r}
# SEM = (Upper limit - Lower limit) / 2
# SEM = Upper Limit - Mean
SEM_sz_sf0.9_schwartz1987 = 85.67823213109716 - 80.15773063582003

# SEM = Mean - Lower limit
SEM_c_sf0.9_schwartz1987 = 76.40378395835765 - 71.98737669712817

# SEM = se

# calculate es
schwartz_1987_es_scrap <- esc_mean_se(grp1m = 76.40378395835765, grp2m = 80.15773063582003, 
            grp1se = SEM_c_sf0.9_schwartz1987, grp2se = SEM_sz_sf0.9_schwartz1987, 
            grp1n = 15, grp2n = 19, 
            es.type = "g")
schwartz_1987_es_scrap


```

## Summarizing table

```{r}
schwartz_1987 <- tibble(es = schwartz_1987_es_scrap$es, se = schwartz_1987_es_scrap$se ) 

schwartz_1987$study <- "Schwartz et al. 1987"
schwartz_1987$method <- "staircase"
schwartz_1987$medication <- "medicated" #all medicated
schwartz_1987$cpz <- NA
schwartz_1987$task <- "flicker/pattern detection"
schwartz_1987$all_SF <- "0.9, 3.8, 15"
schwartz_1987$SF <- 0.9
schwartz_1987$size <- NA
schwartz_1987$BPRS <- NA
schwartz_1987$motion <- 0.8 # in Hz, 0Hz is not depicted in graphs 
schwartz_1987$duration <- NA
schwartz_1987$location <- 0
schwartz_1987$lapses <- FALSE 
schwartz_1987$calculation_statistic <- "m and se"  
schwartz_1987$calculation_data <- "scrapping" 
schwartz_1987$calculation_certainty <- "unsure" #scale is "sure", "unsure", "very unsure"

schwartz_1987
```
