---
title: "Calderone et al., 2013"
output: html_notebook
---

# Effect size

## Gathering information:

Participants:
1) Schizophrenia n = 15

2)  Control n = 15


Contrast sensitivity (p4)
1) Significant main effects of Group
F(1,56) = 11.769 , p \< 0.005

2)  Significant Group x Condition(SF) interaction
F(1,56) = 4.632 , p \< 0.05


Contrast sensitivity in fMRI (p5)
3) SF = 0.5 at 32ms:
Controls: mean = 54.69 , sd = 17.03
Scz: mean = 50.70 , sd = 19.15

4) SF = 4 at 500 ms:
Controls: mean = 41.43 , sd = 24.17
Scz: mean = 23.52 , sd = 21.68


## Calculate effect size:
use the F-statistic (see bookdown.org)

###  Significant main effects of Group (2 groups)
F(1,56) = 11.769 , p \< 0.005
```{r}
calderone_2013_es_f <- esc_f(f = 11.769,      # F value of the one-way anova
      grp1n = 15,   # sample size of group 1 
      grp2n = 15,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD
calderone_2013_es_f
```

### Scrapping data from Figure 3
See Figure 3 for mean contrast sensitivity - problem: scale of y-axis is weird, plotdigitizer cannot compute data correctly.
If I put the y-axis scale y1=0, y2=1000 and choose log10 - plotdigitizer does not give me any values for y.
If I put the y-axis scale y1=0, y2=1000 and choose linear - I get values for y, but they are all wrong.
If I put the y-axis scale y1=100, y2=1000 and choose log10 - I get values for y, but I think they are incorrect as well, because then the intercept of y-axis with x-axis is considered 10 instead of 0.
Thus, I think it is not possible to retrieve correct data from the figure. 


### FMRI results
5 controls were outliers - removed from data n=10
1 patient was outlier - removed from data n=14

3) SF = 0.5 at 32ms:
Controls: mean = 54.69 , sd = 17.03
Scz: mean = 50.70 , sd = 19.15
```{r}
calderone_2013_es_fmri_sf0.5 <- esc_mean_sd(grp1m = 54.69, grp2m = 50.70,  # group mean
            grp1sd = 17.03, grp2sd = 19.15, # group sd
            grp1n = 10, grp2n = 14, 
            es.type = "g")
calderone_2013_es_fmri_sf0.5
```


## Summarizing table

```{r}
calderone_2013 <- tibble(es = calderone_2013_es_f$es, se = calderone_2013_es_f$se ) 

calderone_2013$study <- "Calderone et al. 2013"
calderone_2013$method <- "up-down transform rule" #UDTR
calderone_2013$medication <- "medicated" #all medicated
calderone_2013$cpz <- 783.33
calderone_2013$task <- "2AFC" #2AFC mentioned in the article
calderone_2013$all_SF <- "0.5, 4"
calderone_2013$SF <- 0.5
calderone_2013$size <- "6 x 6" 
calderone_2013$BPRS <- NA
calderone_2013$motion <- FALSE 
calderone_2013$duration <- "0.032 for SF=0.5, 0.5 for SF=4" 
calderone_2013$location <- NA
calderone_2013$lapses <- FALSE 
calderone_2013$calculation_statistic <- "f-statistic"  
calderone_2013$calculation_data <- "reported" 
calderone_2013$calculation_certainty <- "very unsure" #scale is "sure", "unsure", "very unsure"

calderone_2013
```


## Side note 1
This study also measures contrast sensitivity with fMRI and get m and sd.
I am not sure how to interpret these results, or if we can use them instead of the f-statistic.

## Side note 2
The f-statistic has weird df, not sure if we can use this.

## Side note 3
I tried scrapping data from figure 3.
See Figure 3 for mean contrast sensitivity - problem: scale of y-axis is weird, plotdigitizer cannot compute data correctly.
If I put the y-axis scale y1=0, y2=1000 and choose log10 - plotdigitizer does not give me any values for y.
If I put the y-axis scale y1=0, y2=1000 and choose linear - I get values for y, but they are all wrong.
If I put the y-axis scale y1=100, y2=1000 and choose log10 - I get values for y, but I think they are incorrect as well, because then the intercept of y-axis with x-axis is considered 10 instead of 0.
Thus, I think it is not possible to retrieve correct data from the figure. 
Can you take a look at this please?
