---
title: "Cadenhead et al., 2013"
output: html_notebook
---

# Effect size

## Gathering information:

Participants:
1) Schizophrenia n = 53
7 excluded for the contrast sensitivity: n = 46

2)  Control n = 53

3)  Schizotypical personality disorder (SPD) n = 22
1 excluded for the contrast sensitivity: n = 21

Contrast sensitivity (p4)
1) Significant main effects of Group
F(2,118) = 8.81 , p \< 0.001
post-hoc t-test:
Control vs SPD: p \< 0.05 (significant)
Control vs Scz: p \< 0.001 (significant)
SPD vs Scz: not significant

2)  Group x stimulus condition interaction (not significant)
F(2,117) = 0.56 , NS

## Calculate effect size
### Scrapping data from Figure 1 - Luminance (light/dark) contrast sensitivity
Control (n=53): mean = 1.8917784577666974 , SEM = (1.8582215422333028 - 1.9211409988770967)
Scz (n=46): mean = 1.7617449780411711 , SEM = (1.723993304054895 - 1.7911073271366271)
```{r}
#SEM = (upper limit - lower limit) / 2
SEM_c_cadenhead2013 = (1.9211409988770967 - 1.8582215422333028) / 2
SEM_sz_cadenhead2013 = (1.7911073271366271 - 1.723993304054895) / 2

# SEM = se

# calculate es
cadenhead_2013_es <- esc_mean_se(grp1m = 1.8917784577666974, grp2m = 1.7617449780411711, 
            grp1se = SEM_c_cadenhead2013, grp2se = SEM_sz_cadenhead2013, 
            grp1n = 53, grp2n = 46, 
            es.type = "g")
cadenhead_2013_es

```


## Summarizing table

```{r}
cadenhead_2013 <- tibble( es = cadenhead_2013_es$es, se = cadenhead_2013_es$se ) 
cadenhead_2013

cadenhead_2013$study <- "Cadenhead et al. 2013"
cadenhead_2013$method <- "constant stimuli paradigm"  
cadenhead_2013$medication <- "medicated and unmedicated" #n=41 medicated, n=5 unmedicated
cadenhead_2013$cpz <- NA  
cadenhead_2013$task <- "2AFC" 
cadenhead_2013$all_SF <- 1.22
cadenhead_2013$SF <- 1.22
cadenhead_2013$size <- 1.64
cadenhead_2013$BPRS <- NA
cadenhead_2013$motion <- TRUE 
cadenhead_2013$duration <- 0.12 
cadenhead_2013$location <- 2.28 # 2.28° left or right from fixation cross 
cadenhead_2013$lapses <- FALSE  
cadenhead_2013$calculation_statistic <- "m and se"  
cadenhead_2013$calculation_data <- "scrapping, calculate se" 
cadenhead_2013$calculation_certainty <- "unsure" #scale is "sure", "unsure", "very unsure"

cadenhead_2013
```

## Side note 1
F-statistic cannot be used, since it includes 3 groups.

Mean and SEM-interval retrieved from Figure 1 (luminance). Calculation of the SEM = se. Calculation of effect size with m and se.
