---
title: "Shoshina, Mukhitova et al., 2021"
output: html_notebook
---

# Effect size

## Gathering information:

Participants:
1) Schizophrenia n = 68

2) Control n = 30

3) Depression n = 25


Contrast sensitivity (p4)
1) SF = Low (0.4 and 0.6)
Control: mean = 17.8 ; sd = 5.3
Schizophrenia: mean = 12.06 ; sd = 5.3

2)  SF = Medium (1.0 and 4.0)
Control: mean = 21.4 ; sd = 8.1
Schizophrenia: mean = 12.6 ; sd = 5.5

3)  SF = High (10.0)
Control: mean = 7.9 ; sd = 4.6
Schizophrenia: mean = 4.2 ; sd = 2.9


## Calculate effect size:
Calculate based on mean and SD

### SF = Low
1) SF = Low (0.4 and 0.6)
Control: mean = 17.8 ; sd = 5.3
Schizophrenia: mean = 12.06 ; sd = 5.3
```{r}
shoshina_mukhitova_2021_es_low <- esc_mean_sd(grp1m =17.8 , grp2m = 12.06, 
            grp1sd = 5.3, grp2sd = 5.3, 
            grp1n = 30, grp2n = 68, 
            es.type = "g")
shoshina_mukhitova_2021_es_low
```


### SF = Medium
2)  SF = Medium (1.0 and 4.0)
Control: mean = 21.4 ; sd = 8.1
Schizophrenia: mean = 12.6 ; sd = 5.5
```{r}
shoshina_mukhitova_2021_es_medium <- esc_mean_sd(grp1m = 21.4, grp2m = 12.6,
            grp1sd = 8.1, grp2sd = 5.5, 
            grp1n = 30, grp2n = 68, 
            es.type = "g")
shoshina_mukhitova_2021_es_medium
```


### SF = High
3)  SF = High (10.0)
Control: mean = 7.9 ; sd = 4.6
Schizophrenia: mean = 4.2 ; sd = 2.9
```{r}
shoshina_mukhitova_2021_es_high <- esc_mean_sd(grp1m = 7.9, grp2m = 4.2, 
            grp1sd = 4.6, grp2sd = 2.9, 
            grp1n = 30, grp2n = 68, 
            es.type = "g")
shoshina_mukhitova_2021_es_high
```

## Summarizing table
```{r}
shoshina_mukhitova_2021 <- tibble(es = shoshina_mukhitova_2021_es_low$es, se = shoshina_mukhitova_2021_es_low$se ) 

shoshina_mukhitova_2021$study <- "Shoshina, Mukhitova et al. 2021"
shoshina_mukhitova_2021$method <- "staircase"
shoshina_mukhitova_2021$medication <- "medicated" #all medicated
shoshina_mukhitova_2021$cpz <- NA
shoshina_mukhitova_2021$task <- "2AFC"
shoshina_mukhitova_2021$all_SF <- "0.4, 0.6, 1.0, 4.0, 10.0" 
shoshina_mukhitova_2021$SF <- 0.4
shoshina_mukhitova_2021$size <- NA
shoshina_mukhitova_2021$BPRS <- NA
shoshina_mukhitova_2021$motion <- FALSE 
shoshina_mukhitova_2021$duration <- NA
shoshina_mukhitova_2021$location <- 0
shoshina_mukhitova_2021$lapses <-  FALSE
shoshina_mukhitova_2021$calculation_statistic <- "m and sd, low SF (0.4 and 0.6)"  
shoshina_mukhitova_2021$calculation_data <- "reported" 
shoshina_mukhitova_2021$calculation_certainty <- "sure" #scale is "sure", "unsure", "very unsure"

shoshina_mukhitova_2021
```


# Side note 1
Unsure whether sd or se.
SD: Effect Size:   1.0745
 Standard Error:   0.2324
 
SE: Effect Size:   0.1442
 Standard Error:   0.2194 
 
I think it is wrong if the standard error of the effect size is larger than the effect size itself. So I think it is SD.
