---
title: "Schwartz et al., 1987"
output: html_notebook
---

# Effect size

## Gathering information:

Participants: 
1) Schizophrenia
  n = 19
    
2) Control
  n = 15


Contrast sensitivity (p6)
1) Main effect of groups for Pattern detection (0Hz)
F(1,32) = 1.77 , p = 0.2

2) Main effects of SF (not significant for any SF)
  F(1,32) = 2.51 , p = 0.12

3) Interaction SF x groups (not significant)
  F(2,64) = 0.94 , p = 1.397
  

## Calculate effect size:
  use the F-statistic (see bookdown.org)

### Main effects of group (2 groups)
 F(1,32) = 1.77 , p = 0.2
```{r}
schwartz_1987_es <- esc_f(f = 1.77,      # F value of the one-way anova
      grp1n = 19,   # sample size of group 1 
      grp2n = 15,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD
schwartz_1987_es
```  

### Main effects of SF (not significant for any SF) (2 groups)
  F(1,32) = 2.51 , p = 0.12
```{r}
schwartz_1987_es_sf <- esc_f(f = 2.51,      # F value of the one-way anova
      grp1n = 19,   # sample size of group 1 
      grp2n = 15,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD
schwartz_1987_es_sf
```


## Summarizing table
```{r}
schwartz_1987 <- tibble(es = schwartz_1987_es$es, se = schwartz_1987_es$se ) 

schwartz_1987$study <- "Schwartz et al. 1987"
schwartz_1987$method <- "staircase"
schwartz_1987$medication <- "medicated" #n=19 medicated
schwartz_1987$cpz <- NA
schwartz_1987$task <- "flicker/pattern detection"
schwartz_1987$SF <- "0.9, 3.8, 15"
schwartz_1987$size <- NA
schwartz_1987$BPRS <- NA
schwartz_1987$motion <- FALSE 
schwartz_1987$duration <- NA
schwartz_1987$location <- 0
schwartz_1987$lapses <- FALSE 
schwartz_1987$calculation_statistic <- "f-statistic"  
schwartz_1987$calculation_data <- "reported" 
schwartz_1987$calculation_certainty <- "unsure" #scale is "sure", "unsure", "very unsure"

schwartz_1987
```


## Side note 1
Not sure which data to use. Maybe even need to retrieve data from Figure 1.

