---
title: "Schwartz et al., 1987"
output: html_notebook
---

# Effect size

## Gathering information:

Participants: 
1) Schizophrenia
  n = 19
    
2) Control
  n = 15


Contrast sensitivity (p6)
1) Main effects (not significant for any SF)
  F(1,32) = 2.51 , p = 0.12

2) Interaction SF x groups (not significant)
  F(2,64) = 0.94 , p = 1.397


## Calculate effect size:
  use the F-statistic (see bookdown.org)
  
1) Main effects (not significant for any SF)
  F(1,32) = 2.51 , p = 0.12
```{r}
library(esc)
esc_f(f = 2.51,      # F value of the one-way anova
      grp1n = 19,   # sample size of group 1 
      grp2n = 15,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD

```


2) Interaction SF x groups (not significant)
  F(2,64) = 0.94 , p = 1.397
```{r}
library(esc)
esc_f(f = 0.94,      # F value of the one-way anova
      grp1n = 19,   # sample size of group 1 
      grp2n = 15,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD

```

## Side note 1
Is it necessary to calculate the effect size of non-significant results?
