---
title: "Slaghuis, 1998"
output: html_notebook
---

# Effect size

## Gathering information:

Participants: 
1) Schizophrenia
  n = 30
    -> n = 15 with positive symptoms
    -> n = 15 with negative symptoms

2) Control
  n = 15


Contrast sensitivity (p5, experiment 1)
1) Significant main effects of Group (3 groups)
  F(2,42) = 21.7 , p < 0.0001
    -> Post-hoc Tukey HSD
    p < 0.01

2) Significant main effects of duration
  F(1,42) = 1209.6 , p < 0.0001

3) Significant main effects of SF (spatial frequency)
  F(5,210) = 275.5 , p < 0.0001

4) Group x stimulus duration interaction (not significant)
  F(2,42) = 0.316 , p > 0.05
  
5) Significant Group x SF interaction
  F(10,210) = 3.4 , p < 0.0005

6) Significant SF x stimulus duration interaction
  F(5,210) = 41.3 , p < 0.001

7) Groups x stimulus duration x SF (not significant)
  F(10,210) = 0.63 , p > 0.05
  

Experiment 2 = motion contrast sensitivity


## Calculate effect size:
  use the F-statistic (see bookdown.org)
  
1) Significant main effects of Group (3 groups)
  F(2,42) = 21.7 , p < 0.0001


Calculate es by scrapping from Figure 2

Control
SF = 0.4979987983530493 (0.5), mean = 2.0968000196874987
SF = 1.0098677939570224 (1)  , mean = 2.1479999683593762
SF = 2.017920100044738  (2)  , mean = 2.215199965078127
SF = 4.032212488140669  (4)  , mean = 2.1767999669531264
SF = 8.057186938815855  (8)  , mean = 1.888799981015626
SF = 11.991991663525779 (12) , mean = 1.5208000478124977

Positive
SF = 0.4907174609675067 (0.5), mean = 2.0200000234374986
SF = 1.0098677939570224 (1)  , mean = 2.0647999235937537
SF = 2.017920100044738  (2)  , mean = 2.0999999707031263
SF = 4.032212488140669  (4)  , mean = 1.9783999278125035
SF = 8.057186938815855  (8)  , mean = 1.607200043593748
SF = 11.991991663525779 (12) , mean = 1.2199999648437516

Negative
SF = 0.5053874957955264 (0.5), mean = 1.7927999857031256
SF = 1.0098677939570224 (1)  , mean = 1.9432000271874987
SF = 2.017920100044738  (2)  , mean = 1.984799976328126
SF = 4.032212488140669  (4)  , mean = 1.8311999838281259
SF = 8.057186938815855  (8)  , mean = 1.4344000520312474
SF = 11.991991663525779 (12) , mean = 1.072800020859374

I cannot retrieve any other information. Thus, we need to ask for the raw data.





    
```{r}
slaghuis_1998_es <- 
  
slaghuis_1998_es
```


## Summarizing table

```{r}
#slaghuis_1998 <- tibble( es = slaghuis_1998_es$es, se = slaghuis_1998_es$se ) 
slaghuis_1998 <- tibble( es = NA, se = NA )

slaghuis_1998$study <- "Slaghuis. 1998"
slaghuis_1998$method <- "staircase"  
slaghuis_1998$medication <- "medicated" #n=30 medicated
slaghuis_1998$cpz <- 221.65  #Dose is combined mean of group Positive (201.1) and Negative (242.2)
slaghuis_1998$task <- "2AFC" #2AFC mentioned in the article
slaghuis_1998$SF <- "0.5, 1, 2, 4, 8 and 12"
slaghuis_1998$size <- "4.03 x 3.36" #size of the stimulus presented
slaghuis_1998$BPRS <- NA
slaghuis_1998$motion <- FALSE 
slaghuis_1998$duration <- "0.4 or 0.04" #Article says: 40ms or 400ms
slaghuis_1998$location <- 0 
slaghuis_1998$lapses <- TRUE  #If observer noticed a drift in attention, the trial was repeated.
slaghuis_1998$calculation_statistic <- ""  #"t-test", "m and sd"
slaghuis_1998$calculation_data <- "" #"scrapping", "reported", "raw"
slaghuis_1998$calculation_certainty <- "unsure" #scale is "sure", "unsure", "very unsure"

slaghuis_1998
```

## Side note 1
F-statistic contains 3 groups - not applicable.

## Side note 2
I have retrieved the mean for each SF from Figure 2. However, no other data can be retrieved, thus no es can be calculated. Need to ask author for data.




