---
title: "Slaghuis, 1998"
output: html_notebook
---

# Effect size

## Gathering information:

Participants: 
1) Schizophrenia
  n = 30
    -> n = 15 with positive symptoms
    -> n = 15 with negative symptoms

2) Control
  n = 15


Contrast sensitivity (p5, experiment 1)
1) Significant main effects of Group
  F(2,42) = 21.7 , p < 0.0001
    -> Post-hoc Tukey HSD
    p < 0.01

2) Significant main effects of duration
  F(1,42) = 1209.6 , p < 0.0001

3) Significant main effects of SF (spatial frequency)
  F(5,210) = 275.5 , p < 0.0001

4) Group x stimulus duration interaction (not significant)
  F(2,42) = 0.316 , p > 0.05
  
5) Significant Group x SF interaction
  F(10,210) = 3.4 , p < 0.0005

6) Significant SF x stimulus duration interaction
  F(5,210) = 41.3 , p < 0.001

7) Groups x stimulus duration x SF (not significant)
  F(10,210) = 0.63 , p > 0.05
  

Experiment 2 = motion contrast sensitivity


## Calculate effect size:
  use the F-statistic (see bookdown.org)
  
1) Significant main effects of Group
  F(2,42) = 21.7 , p < 0.0001
    -> Post-hoc Tukey HSD
    p < 0.01
```{r}
library(esc)
esc_f(f = 21.7,      # F value of the one-way anova
      grp1n = 30,   # sample size of group 1 
      grp2n = 15,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD

```


2) Significant main effects of duration
  F(1,42) = 1209.6 , p < 0.0001
```{r}
library(esc)
esc_f(f = 1209.6,      # F value of the one-way anova
      grp1n = 30,   # sample size of group 1 
      grp2n = 15,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD

```

3) Significant main effects of SF (spatial frequency)
  F(5,210) = 275.5 , p < 0.0001
```{r}
library(esc)
esc_f(f = 275.5,      # F value of the one-way anova
      grp1n = 30,   # sample size of group 1 
      grp2n = 15,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD

```

4) Group x stimulus duration interaction (not significant)
  F(2,42) = 0.316 , p > 0.05
```{r}
library(esc)
esc_f(f = 0.316,      # F value of the one-way anova
      grp1n = 30,   # sample size of group 1 
      grp2n = 15,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD
 
```

5) Significant Group x SF interaction
  F(10,210) = 3.4 , p < 0.0005
```{r}
library(esc)
esc_f(f = 3.4,      # F value of the one-way anova
      grp1n = 30,   # sample size of group 1 
      grp2n = 15,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD
 
```


6) Significant SF x stimulus duration interaction
  F(5,210) = 41.3 , p < 0.001
```{r}
library(esc)
esc_f(f = 41.3,      # F value of the one-way anova
      grp1n = 30,   # sample size of group 1 
      grp2n = 15,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD

```


7) Groups x stimulus duration x SF (not significant)
  F(10,210) = 0.63 , p > 0.05
```{r}
library(esc)
esc_f(f = 0.63,      # F value of the one-way anova
      grp1n = 30,   # sample size of group 1 
      grp2n = 15,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD

```