---
title: "Kéri et al., 2002"
output: html_notebook
---

# Effect size

## Gathering information:

Participants: 
1) Schizophrenia
  n = 20

2) Control
  n = 15


Contrast sensitivity (p4)
1) Significant main effects of Group
  F(1,33) = 13.93 , p < 0.001

2) Significant main effects of SF (spatial frequency)
  F(8,264) = 131.78 , p < 0.0001

3) Significant Group x SF interaction
  F(8,264) = 2.28 , p < 0.05
  -> Post-hoc comparison
  See Figure 3 (mean and standard deviation) + 
  Table 2 (P-values and correlation coefficients)
  

Dynamic contrast sensitivity (Is this motion sensitivity?)


## Calculate effect size:
  use the F-statistic (see bookdown.org)
  
1) Significant main effects of Group
  F(1,33) = 13.93 , p < 0.001
```{r}
library(esc)
esc_f(f = 13.93,      # F value of the one-way anova
      grp1n = 20,   # sample size of group 1 
      grp2n = 15,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD

```

2) Significant main effects of SF (spatial frequency)
  F(8,264) = 131.78 , p < 0.0001
```{r}
library(esc)
esc_f(f = 131.78,      # F value of the one-way anova
      grp1n = 20,   # sample size of group 1 
      grp2n = 15,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD

```

3) Significant Group x SF interaction
  F(8,264) = 2.28 , p < 0.05
```{r}
library(esc)
esc_f(f = 2.28,      # F value of the one-way anova
      grp1n = 20,   # sample size of group 1 
      grp2n = 15,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD

```

## Side note 1
The authors also look at dynamic contrast sensitivity. I think this is motion sensitivity, therefore I did not calculate the effect size.

## Side note 2
I did not calculate the effect size for the post-hoc analysis, since it is a figure and I am not sure how to retrieve information from this. It also has a table with p-values, I'm not sure if the formula for extracting effect size from p-values is allowed in this case. 

