---
title: "Chen et al., 2003"
output: html_notebook
---

# Effect size

## Gathering information:

Participants:
1) Schizophrenia n = 45
n = 12 with schizophrenia
n = 33 with schizoaffective disorder
also classified according to type of antipsychotic medication

2)  Control n = 39

3)  First-degree relatives n = 24


Contrast sensitivity (p3)
1) Schizophrenia group (as a whole) vs healthy controls (significant)
scz: mean = 0.0036 ; SD = 0.0039
ctrl: mean = 0.0025 ; SD = 0.0016 
t = 2.04, df = 82, p\<0.05
Effect size of group difference: 0.71 (small) (maybe relatives as a group also included, not stated in paper)

2)  Classified schizophrenia patients by type of antipsychotic medication (not neccessary for us)

3)  First degree relatives vs healthy controls (not significant)
rel: mean = 0.0022 ; SD = 0.001
ctrl: mean = 0.0025 ; SD = 0.0016

## Calculate effect size:

use the means, the standards deviations and sample sizes (see tutorials meta-analysis)

1)  Schizophrenia group (as a whole) vs healthy controls
scz: mean = 0.0036 ; SD = 0.0039
ctrl: mean = 0.0025 ; SD = 0.0016

```{r}
chen_2003_es <- esc_mean_sd(grp1m = 0.0036, grp2m = 0.0025, 
            grp1sd = 0.0039, grp2sd = 0.0016, 
            grp1n = 45, grp2n = 39, 
            es.type = "g")
chen_2003_es

```

1)  Schizophrenia group (as a whole) vs healthy controls scz:
t = 2.04, df = 82, p\<0.05
```{r}
chen_2003_t_statistic <- esc_t(t = 2.04,
      grp1n = 45,
      grp2n = 39,
      es.type = "g")
chen_2003_t_statistic
```

3)  First degree relatives vs healthy controls (not significant)
rel: mean = 0.0022 ; SD = 0.001
ctrl: mean = 0.0025 ; SD = 0.0016

```{r}
chen_2003_es_rel <- esc_mean_sd(grp1m = 0.0022, grp2m = 0.001, 
            grp1sd = 0.0039, grp2sd = 0.0016, 
            grp1n = 24, grp2n = 39, 
            es.type = "g")
chen_2003_es_rel
```

## Summarizing table

```{r}
chen_2003 <- tibble( es = chen_2003_es$es, se = chen_2003_es$se ) 
chen_2003

chen_2003$study <- "Chen et al. 2003"
chen_2003$method <- "NA" # adaptative, mc, ... (Do they use a special method to display contrast?) 
chen_2003$medication <- "?" #TRUE #n=39 were on medication, n=6 not on medication
chen_2003$cpz <- "NA"  #Dose is not mentioned
chen_2003$task <- "2AFC" #2AFC means two alternative forced choice
chen_2003$SF <- 0.5
chen_2003$BPRS <- 42.4
chen_2003$motion <- TRUE #is grating moving?
chen_2003$duration <- 0.3 #Duration of the stimulus in seconds
chen_2003$location <- 0 #Where the stimulus was presented in degrees of visual angle (fixation = 0)
chen_2003$lapses <- "?"  #In lapses, we can include whether they control for lapses (TRUE) or not (FALSE).
chen_2003$calculation_statistic <- "m and sd"  #"t-test", "m and sd"
chen_2003$calculation_data <- "reported" #"scrapping", "reported", "raw"
chen_2003$calculation_certainty <- "unsure" #scale is "sure", "unsure", "very unsure"

chen_2003
```

## Side note 1

The authors reported an effect size, however, my calculations do not match this effect size. Am I doing something wrong?

## Side note 2

The authors mention that the grating is moving with a temporal frequency of 5 Hz. Does this mean the study is about motion and not solely contrast detection?

## Side note 3

The authors also do contrast sensitivity calculations based on the type on antipsychotic medication. I did not calculate these effect sizes, since I don't believe it is relevant.
