---
title: "Slaghuis, 2004"
output: html_notebook
---

# Effect size

## Gathering information:

Participants: 1) Schizophrenia n = 28 -\> n = 14 with positive symptoms -\> n = 14 with negative symptoms

2)  Control n = 14

Contrast sensitivity (p6, experiment 1) 1) Significant main effects of Group F(2,37) = 30.90 , p \< 0.0005

2)  Significant main effects of temporal frequency F(2,70) = 22.57 , p \< 0.0005

3)  Significant main effects of SF (spatial frequency) F(3,79) = 38.72 , p \< 0.0005

4)  Group x temporal frequency interaction (not significant) F(4,77) = 0.77 , p \> 0.05

5)  Significant Group x SF interaction F(5,79) = 2.30 , p \> 0.05 (the article reports this as significant, I think they made a mistake here)

6)  Significant SF x temporal frequency interaction F(6,191) = 5.42 , p \< 0.0005

7)  Significant Groups x temporal frequency x SF interaction F(11,191) = 1.96 , p \< 0.04

## Calculate effect size:

use the F-statistic (see bookdown.org)

1)  Significant main effects of Group F(2,37) = 30.90 , p \< 0.0005

```{r}
library(esc)
esc_f(f = 30.90,      # F value of the one-way anova
      grp1n = 28,   # sample size of group 1 
      grp2n = 14,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD

```

2)  Significant main effects of temporal frequency F(2,70) = 22.57 , p \< 0.0005

```{r}
library(esc)
esc_f(f = 22.57,      # F value of the one-way anova
      grp1n = 28,   # sample size of group 1 
      grp2n = 14,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD

```

3)  Significant main effects of SF (spatial frequency) F(3,79) = 38.72 , p \< 0.0005

```{r}
library(esc)
esc_f(f = 38.72,      # F value of the one-way anova
      grp1n = 28,   # sample size of group 1 
      grp2n = 14,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD

```

4)  Group x temporal frequency interaction (not significant) F(4,77) = 0.77 , p \> 0.05

```{r}
library(esc)
esc_f(f = 0.77,      # F value of the one-way anova
      grp1n = 28,   # sample size of group 1 
      grp2n = 14,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD
 
```

5)  Significant Group x SF interaction F(5,79) = 2.30 , p \> 0.05 (the article reports this as significant, I think they made a mistake here)

```{r}
library(esc)
esc_f(f = 2.30,      # F value of the one-way anova
      grp1n = 28,   # sample size of group 1 
      grp2n = 14,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD
 
```

6)  Significant SF x temporal frequency interaction F(6,191) = 5.42 , p \< 0.0005

```{r}
library(esc)
esc_f(f = 5.42,      # F value of the one-way anova
      grp1n = 28,   # sample size of group 1 
      grp2n = 14,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD

```

7)  Significant Groups x temporal frequency x SF interaction F(11,191) = 1.96 , p \< 0.04

```{r}
library(esc)
esc_f(f = 1.96,      # F value of the one-way anova
      grp1n = 28,   # sample size of group 1 
      grp2n = 14,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD

```
