---
title: "Chen et al., 2005"
output: html_notebook
---

## Comments

The relevant task is the contrast detection task. They only provide the F for the four groups, so it is not possible to calculate the g for the schizophrenia and control group. We need to ask for the data.

Asked for the data, authors have died so we do not have access to the data.

## More information

In lapses, we can include whether they control for lapses (TRUE) or not (FALSE).

```{r}
dat_chen_2005$lapses <- FALSE
```

Is the grating moving?

```{r}
dat_chen_2005$motion <- TRUE
```

Spatial frequency in degrees of visual angle

```{r}
dat_chen_2005$sf <- 0.5
```

Duration of the stimulus in seconds

```{r}
dat_chen_2005$duration <- 0.3
```

Where the stimulus was presented in degrees of visual angle (fixation = 0)

```{r}
dat_chen_2005$location <- 0
```

Do they use a special method to display contrast?

```{r}
dat_chen_2005$method <- NA
```

# Effect size

## Gathering information:

Participants: 1) Schizophrenia/schizoaffective disorder n = 29

2)  First degree relatives of schizophrenic patients n = 20

3)  Bipolar disorder n = 19

4)  Control n = 33

Contrast sensitivity (p6-7) 1) Effect of group (not significant) F = 1.21 , p = 0.3123 , df = 3

## Calculate effect size:

use the F-statistic (see bookdown.org)

1)  Effect of group (not significant) F = 1.21 , p = 0.3123 , df = 3

```{r}
#The relevant task is the contrast detection task. They only provide the F for the four groups, so it is not possible to calculate the g for the schizophrenia and control group. We need to ask for the data.

#Asked for the data, authors have died so we do not have access to the data.
```

## Summarizing table

```{r}
chen_2005 <- tibble(es = "No data", se = "No data" ) 
chen_2005

chen_2005$study <- "Chen et al. 2005"
chen_2005$method <- "?spatial luminance moduation?" # adaptative, mc, ... (Do they use a special method to display contrast?)
chen_2005$medication <- "?" #TRUE #n=28 were on medication, n=1 not on medication
chen_2005$cpz <- "557"  #in mg
chen_2005$task <- "2AFC" #2AFC means two alternative forced choice
chen_2005$SF <- 0.5
chen_2005$BPRS <- 40.0
chen_2005$motion <- TRUE #is grating moving?
chen_2005$duration <- 0.3 #Duration of the stimulus in seconds
chen_2005$location <- 0 #Where the stimulus was presented in degrees of visual angle (fixation = 0)
chen_2005$lapses <- "FALSE"  #In lapses, we can include whether they control for lapses (TRUE) or not (FALSE).
chen_2005$calculation_statistic <- "No data"  #"t-test", "m and sd"
chen_2005$calculation_data <- "No data" #"scrapping", "reported", "raw"
chen_2005$calculation_certainty <- "sure" #scale is "sure", "unsure", "very unsure"

chen_2005
```
