---
title: "Butler et al, 2005"
output: html_notebook
---

# Effect size

## Gathering information:

Participants:
1) Schizophrenia n = 33 
n = 27 with schizophrenia
n = 6 with schizoaffective disorder

2)  Control n = 21

Contrast sensitivity (p5)
1) Significant between-group effect (2 groups)
F(1,49) = 81.6 , p\<0.001

2)  Significant group x spatial frequency interaction
F(6,44) = 13.1 , p\<0.001

## Calculate effect size:

use the F-statistic (see bookdown.org)

1)  Significant between-group effect (2 groups)
F(1,49) = 81.6 , p\<0.001

```{r}
butler_2005_es <- esc_f(f = 81.6,      # F value of the one-way anova
      grp1n = 33,   # sample size of group 1 
      grp2n = 21,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD
butler_2005_es
```

Scrapping data from Figure 4 (plotdigitizer)
No error bars to be seen, only able to get mean. => no calculation of es possible through scrapping

## Summarizing table

```{r}
butler_2005 <- tibble( es = butler_2005_es$es, se = butler_2005_es$se ) 

butler_2005$study <- "Butler et al. 2005"
butler_2005$method <- "up-and-down transformed response"  
butler_2005$medication <- "medicated" #n=33 medicated
butler_2005$cpz <- 1194.0 
butler_2005$task <- "2AFC" #2AFC mentioned in the article
butler_2005$SF <- "0.5, 1.0, 2.0, 4.0, 7.0, 10.0, 21.0"
butler_2005$size <- "8 x 8" 
butler_2005$BPRS <- 36.9
butler_2005$motion <- FALSE 
butler_2005$duration <- 0.032 
butler_2005$location <- 5.7
butler_2005$lapses <- TRUE # experimenter (not participant) pressed the buttons to indicate whether stimulus on left or right side 
butler_2005$calculation_statistic <- "f-statistic"  
butler_2005$calculation_data <- "reported" 
butler_2005$calculation_certainty <- "unsure" #scale is "sure", "unsure", "very unsure"

butler_2005
```

## Side note 1
An es of 2.4 seems very high. Is this correct?
