---
title: "Chen et al., 2005"
output: html_notebook
---

## Comments

It is not necessary to include the package `esc` many times. I included it in the file 00_funs.Rmd. So you can run first this file and then all the packages will be activated.

The relevant task is the contrast detection task. The only provide the F for the four groups, so it is not possible to calculate the g for the schizophrenia and control group. We need to ask for the data.

## More information

In lapses, we can include whether they control for lapses (TRUE) or not (FALSE).

```{r}
dat_chen_2005$lapses <- FALSE
```

Is the grating moving?

```{r}
dat_chen_2005$motion <- TRUE
```

Spatial frequency in degrees of visual angle

```{r}
dat_chen_2005$sf <- 0.5
```

Duration of the stimulus in seconds

```{r}
dat_chen_2005$duration <- 0.3
```

Where the stimulus was presented in degrees of visual angle (fixation = 0)

```{r}
dat_chen_2005$location <- 0
```

Do they use a special method to display contrast?

```{r}
dat_chen_2005$method <- NA
```

# Effect size

## Gathering information:

Participants: 1) Schizophrenia/schizoaffective disorder n = 29

2)  First degree relatives of schizophrenic patients n = 20

3)  Bipolar disorder n = 19

4)  Control n = 33

Contrast sensitivity (p6-7) 1) Effect of group (not significant) F = 1.21 , p = 0.3123 , df = 3

## Calculate effect size:

use the F-statistic (see bookdown.org)

1)  Effect of group (not significant) F = 1.21 , p = 0.3123 , df = 3

```{r}
library(esc)
esc_f(f = 1.21,      # F value of the one-way anova
      grp1n = 29,   # sample size of group 1 
      grp2n = 33,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD

```

## Side note 1

I don't know which group sizes to use. I believe they performed ANOVA on all 4 groups, thus I am not sure if it is allowed to only use the sample sizes of the schizophrenia and control groups.

## Side note 2

I use the sample size of the complete schizophrenia group (schizophrenia + schizoaffected disorder). Is this correct?
