---
title: "Butler et al, 2005"
output: html_notebook
---

# Effect size

## Gathering information:

Participants: 1) Schizophrenia n = 33 -\> n = 27 with schizophrenia -\> n = 6 with schizoaffective disorder

2)  Control n = 21

Contrast sensitivity (p5) 1) Significant between-group effect F(1,49) = 81.6 , p\<0.001

2)  Significant group x spatial frequency interaction F(6,44) = 13.1 , p\<0.001

## Calculate effect size:

use the F-statistic (see bookdown.org)

1)  Significant between-group effect F(1,49) = 81.6 , p\<0.001

```{r}
library(esc)
esc_f(f = 81.6,      # F value of the one-way anova
      grp1n = 33,   # sample size of group 1 
      grp2n = 21,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD

```

2)  Significant group x spatial frequency interaction F(6,44) = 13.1 , p\<0.001

```{r}
library(esc)
esc_f(f = 13.1,      # F value of the one-way anova
      grp1n = 33,   # sample size of group 1 
      grp2n = 21,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD

```
