---
title: "Chen et al., 2006"
output: html_notebook
---

# Effect size

## Gathering information:

Participants: 
1) Schizophrenia
  n = 25

2) Control
  n = 25
  
3) Bipolar disorder
  n = 16


Contrast sensitivity (p5, experiment d)
t-statistic
1) Bipolar vs control (not significant)
  Bipolar: mean = 0.0027 ; sd = 0.0017
  Control: mean = 0.0039 ; sd = 0.0027
  -> t(1,37) = 1.5 , p = 0.143

2) Schizophrenia vs control (not significant)
  Schizophrenia: mean = 0.0036 ; sd = 0.0020
  Control: mean = 0.0039 ; sd = 0.0027
  -> t(1,44) = 0.49 , p = 0.627

3) Schizophrenia vs bipolar (not significant)
  Schizophrenia: mean = 0.0036 ; sd = 0.0020
  Bipolar: mean = 0.0027 ; sd = 0.0017
  -> t(1,38) = 1.4 , p = 0.108
  

## Calculate effect size:
  use the mean and sd (see bookdown.org)
  use the t-statistic
  
2) Schizophrenia vs control (not significant)
  Schizophrenia: mean = 0.0036 ; sd = 0.0020
  Control: mean = 0.0039 ; sd = 0.0027
```{r}
chen_2006_es <- esc_mean_sd(grp1m = 0.0036, grp2m = 0.0039,  # group mean
            grp1sd = 0.0020, grp2sd = 0.0027, # group sd
            grp1n = 25, grp2n = 25, 
            es.type = "g")
chen_2006_es

```

2) Schizophrenia vs control (not significant)
  -> t(1,44) = 0.49 , p = 0.627
```{r}
chen_2006_es_t <- esc_t(t = 0.49, # t-statistic
      grp1n = 25,
      grp2n = 25,
      es.type = "g")
chen_2006_es_t

```


## Summarizing table

```{r}
chen_2006 <- tibble( es = chen_2006_es$es, se = chen_2006_es$se ) 
chen_2006

chen_2006$study <- "Chen et al. 2006"
chen_2006$method <- "staircase" # adaptative, mc, ... 
chen_2006$medication <- "medicated and unmedicated" #n=24 medicated, n=1 unmedicated
chen_2006$cpz <- "388"  #in mg
chen_2006$task <- "2AFC" 
chen_2006$SF <- 0.5
chen_2006$size <- 19
chen_2006$BPRS <- 43
chen_2006$motion <- TRUE #is grating moving?
chen_2006$duration <- 0.3 #Duration of the stimulus in seconds
chen_2006$location <- 0 #Where the stimulus was presented in degrees of visual angle (fixation = 0)
chen_2006$lapses <- FALSE #In lapses, we can include whether they control for lapses (TRUE) or not (FALSE).
chen_2006$calculation_statistic <- "m and sd"  #"t-test", "m and sd"
chen_2006$calculation_data <- "reported" #"scrapping", "reported", "raw"
chen_2006$calculation_certainty <- "unsure" #scale is "sure", "unsure", "very unsure"

chen_2006
```



## Side note 1

Why is the effect size different when I calculate it with the m and sd vs when calculated with the t-statistic?
