---
title: "Cimmer et al., 2006"
output: html_notebook
---

# Effect size

## Gathering information:

Participants:
1) Schizophrenia n = 44
n = 32 with non-deficit schizophrenia
n = 12 with deficit schizophrenia

2)  Control n = 20

Contrast sensitivity (p3)
1) Significant main effects of Group
F(2,61) = 14.62 , p \< 0.0001
Tukey's HSD test
p \< 0.001 (schizophrenia vs controls)
p = 0.17 (non-deficit vs deficit)

## Calculate effect size:

use the F-statistic (see bookdown.org)

1)  Significant main effects of Group
F(2,61) = 14.62 , p \< 0.0001 

```{r}
cimmer_2006_es <- esc_f(f = 14.62,      # F value of the one-way anova
      grp1n = 44,   # sample size of group 1 
      grp2n = 20,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD
cimmer_2006_es
```


## Summarizing table

```{r}
cimmer_2006 <- tibble( es = cimmer_2006_es$es, se = cimmer_2006_es$se ) 
cimmer_2006

cimmer_2006$study <- "Cimmer et al. 2006"
cimmer_2006$method <- "luminance modulation" # adaptative, mc, ... (Do they use a special method to display contrast?) 
cimmer_2006$medication <- "TRUE" #all patients were on medication
cimmer_2006$cpz <- "NA"  #Dose is not mentioned
cimmer_2006$task <- "2AFC" #2AFC means two alternative forced choice
cimmer_2006$SF <- 0.5
cimmer_2006$BPRS <- "NA" #not mentioned
cimmer_2006$motion <- TRUE #is grating moving?
cimmer_2006$duration <- 0.5 #Duration of the stimulus in seconds
cimmer_2006$location <- 0 #Where the stimulus was presented in degrees of visual angle (fixation = 0)
cimmer_2006$lapses <- "?"  #In lapses, we can include whether they control for lapses (TRUE) or not (FALSE).
cimmer_2006$calculation_statistic <- "f-statistic"  #"t-test", "m and sd"
cimmer_2006$calculation_data <- "reported" #"scrapping", "reported", "raw"
cimmer_2006$calculation_certainty <- "unsure" #scale is "sure", "unsure", "very unsure"

cimmer_2006
```

## Side note 1
I think Group in the F-statistic is 3 groups (deficit, non-deficit and healthy controls)

## Side note 2
Maybe we can retrieve the correct data from figure 2, and add up both schizophrenia groups (deficit and non-deficit)?