---
title: "O' Donell et al., 2006"
output: html_notebook
---

# Effect size

## Gathering information:

<<<<<<< HEAD
1)  Schizophrenia n = 40 -\> n = 24 with schizophrenia / schizoaffective disorder (SZ) -\> n = 20 with schizophrenia -\> n = 4 with schizoaffective disorder -\> n = 16 with schizotypical personality disorder (SPD)

2)  Control n = 40

Contrast sensitivity (p5) Visual test performance: Mean (SD) 1) Control (static): 1.74 (.45)

2)  SPD (static): 1.76 (.46)

3)  Medicated SZ (static): 1.31 (.53)

4)  Unmedicated SZ (static): 1.45 (.42)

=\> SZ groups showed lowered contrast sensitivity

Contrast sensitivity ANOVA Group vs stimulus (static + motion) (-\> not sure if these results can be used, since the motion contrast sensitivity is also included) 1) Significant main effects of Group F(2,77) = 6.52 , p = 0.002

2)  Significant main effects of Test F(3,231) = 66.1 , p \< 0.001

Follow-up ANOVAs 3) Control vs SPD F(1,54) = 0.14 , p = 0.71

4)  Control vs SZ F(1,62) = 9.67 , p = 0.003

=======
1)  Schizophrenia n = 40
n = 24 with schizophrenia / schizoaffective disorder (SZ) 
-> n = 20 with schizophrenia
-> n = 4 with schizoaffective disorder
n = 16 with schizotypical personality disorder (SPD)

2)  Control n = 40

Contrast sensitivity (p5)
Visual test performance: 
1) Control (static): mean = 1.74 , sd = .45 , n=40

2)  SPD (static): mean= 1.76 , sd= .46 , n=16

3)  Medicated SZ (static): mean= 1.31 , sd= .53 , n=14

4)  Unmedicated SZ (static): mean = 1.45 , sd = .42 , n=10

=\> SZ groups showed lowered contrast sensitivity

Contrast sensitivity ANOVA Group vs stimulus (static + motion) (-\> not sure if these results can be used, since the motion contrast sensitivity is also included)

1) Significant main effects of Group (spd + sz + ctrl)
F(2,77) = 6.52 , p = 0.002

2)  Significant main effects of Test
F(3,231) = 66.1 , p \< 0.001

Follow-up ANOVAs

3) Control vs SPD F(1,54) = 0.14 , p = 0.71

4)  Control vs SZ F(1,62) = 9.67 , p = 0.003

>>>>>>> a87c135bafb5f0c103d404d484586e713d4a0cec
5)  SPD vs SZ F(1,38) = 5.58 , p = 0.02

## Calculate effect size:
?? probably use m and sd, but add up medicated and unmedicated SZ (how?)

<<<<<<< HEAD
=======
F-statistic from follow-up anova
4)  Control vs SZ F(1,62) = 9.67 , p = 0.003
```{r}
oDonnell_2006_es_f <- esc_f(f = 9.67,      # F value of the one-way anova
      grp1n = 40,   # sample size of group 1 
      grp2n = 24,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD
oDonnell_2006_es_f
```



## Summarizing table

```{r}
oDonnell_2006 <- tibble( es = oDonnell_2006_es_f$es, se = oDonnell_2006_es_f$se ) 
oDonnell_2006

oDonnell_2006$study <- "O'Donnell et al. 2006"
oDonnell_2006$method <- "staircase spatial modulation" # adaptative, mc, ... (Do they use a special method to display contrast?) 
oDonnell_2006$medication <- "?" #TRUE #n=14 were on medication, n=10 not on medication
oDonnell_2006$cpz <- "NA"  #Dose is not mentioned
oDonnell_2006$task <- "SGD" #SGD means static grating detection 
oDonnell_2006$SF <- 9.9
oDonnell_2006$BPRS <- "NA"
oDonnell_2006$motion <- FALSE #is grating moving?
oDonnell_2006$duration <- 1.0 #Duration of the stimulus in seconds
oDonnell_2006$location <- 2.9 #Where the stimulus was presented in degrees of visual angle (fixation = 0)
oDonnell_2006$lapses <- "?"  #In lapses, we can include whether they control for lapses (TRUE) or not (FALSE).
oDonnell_2006$calculation_statistic <- "f-statistic"  #"t-test", "m and sd"
oDonnell_2006$calculation_data <- "reported" #"scrapping", "reported", "raw"
oDonnell_2006$calculation_certainty <- "very unsure" #scale is "sure", "unsure", "very unsure"

oDonnell_2006
```


>>>>>>> a87c135bafb5f0c103d404d484586e713d4a0cec
## Side note:

I think we need to ask for the data. I don't know how to compare the results to each other...

For example with the mean and SD, maybe we could compare control vs SPD + medicated SZ + unmedicated SZ, although I'm not sure whether it is allowed to add up the 3 schizophrenia conditions.

Also for the ANOVA: the results contain the factors Stimulus and Group, with Stimulus including static and moving stimuli. Thus, there is not comparison of static alone.
