---
title: "O' Donnell et al., 2006"
output: html_notebook
---

# Effect size

## Gathering information:

Participants
1)  Schizophrenia n = 40
n = 24 with schizophrenia / schizoaffective disorder (SZ) 
-> n = 20 with schizophrenia
-> n = 4 with schizoaffective disorder
n = 16 with schizotypical personality disorder (SPD)

2)  Control n = 40


Contrast sensitivity (p5)
1) Control (static): mean = 1.74 , sd = 0.45 , n=40

2)  SPD (static): mean= 1.76 , sd= 0.46 , n=16

3)  Medicated SZ (static): mean= 1.31 , sd= 0.53 , n=14

4)  Unmedicated SZ (static): mean = 1.45 , sd = 0.42 , n=10

=\> SZ groups showed lowered contrast sensitivity


Contrast sensitivity ANOVA Group vs stimulus (static + motion) (-\> not sure if these results can be used, since the motion contrast sensitivity is also included)
1) Significant main effects of Group (spd + sz + ctrl)
F(2,77) = 6.52 , p = 0.002

2)  Significant main effects of Test
F(3,231) = 66.1 , p \< 0.001


Follow-up ANOVAs of group effect
3) Control vs SPD F(1,54) = 0.14 , p = 0.71

4)  Control vs SZ F(1,62) = 9.67 , p = 0.003

5)  SPD vs SZ F(1,38) = 5.58 , p = 0.02

## Calculate effect size:
use m and sd, but pool medicated and unmedicated SZ

### F-statistic from follow-up anova
4)  Control vs SZ F(1,62) = 9.67 , p = 0.003
```{r}
oDonnell_2006_es_f <- esc_f(f = 9.67,      # F value of the one-way anova
      grp1n = 40,   # sample size of group 1 
      grp2n = 24,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD
oDonnell_2006_es_f
```


### M and sd

1) Control (static): mean = 1.74 , sd = 0.45 , n=40
2)  SPD (static): mean= 1.76 , sd= 0.46 , n=16
3)  Medicated SZ (static): mean= 1.31 , sd= 0.53 , n=14
4)  Unmedicated SZ (static): mean = 1.45 , sd = 0.42 , n=10

First calculate the pooled mean and sd of both SZ groups (medicated and unmedicated) - see side note 2
```{r}
SZ_pooled_oDonnell2006 <- pool.groups(n1 = 14,   # sample size group 1
            n2 = 10,   # sample size group 2
            m1 = 1.31,  # mean group 1
            m2 = 1.45,    # mean group 2
            sd1 = 0.53,   # sd group 1
            sd2 = 0.45) # sd group2 
SZ_pooled_oDonnell2006
```

Now calculate the effect size Control (group1) vs pooled SZ (group2)
Control (static): mean = 1.74 , sd = 0.45 , n=40
```{r}
oDonnell_2006_es <- esc_mean_sd(grp1m = 1.74, grp2m = SZ_pooled_oDonnell2006$Mpooled,  # group mean
            grp1sd = 0.45, grp2sd = SZ_pooled_oDonnell2006$SDpooled, # group sd
            grp1n = 40, grp2n = SZ_pooled_oDonnell2006$Npooled, 
            es.type = "g")
oDonnell_2006_es
```


## Summarizing table

```{r}
oDonnell_2006 <- tibble( es = oDonnell_2006_es$es, se = oDonnell_2006_es$se ) 
oDonnell_2006

oDonnell_2006$study <- "O'Donnell et al. 2006"
oDonnell_2006$method <- "staircase" 
oDonnell_2006$medication <- "medicated and unmedicated" #n=14 medicated, n=10 unmedicated
oDonnell_2006$cpz <- NA  #Dose is not mentioned
oDonnell_2006$task <- "2IFC" # 2 interval forced choice 
oDonnell_2006$all_SF <- 9.9
oDonnell_2006$SF <- 9.9
oDonnell_2006$size <- 8.37
oDonnell_2006$BPRS <- NA
oDonnell_2006$motion <- FALSE 
oDonnell_2006$duration <- 1.0 
oDonnell_2006$location <- 2.9 
oDonnell_2006$lapses <- FALSE  
oDonnell_2006$calculation_statistic <- "m and sd"  
oDonnell_2006$calculation_data <- "reported, pooling sd" 
oDonnell_2006$calculation_certainty <- "sure" #scale is "sure", "unsure", "very unsure"

oDonnell_2006
```

## Side note 1

I believe the f-statistic is not entirely correct. It compares ctrl vs scz, but not sure if this is only for static, or also for motion. - It's a very complex anova, use m and sd.

Calculation of the es through m and sd needed pooling of 2 groups (see side note 2).

## Side note 2
Function dmetar() doesn't want to install, to get the function pool.groups() working, copy code below in console and run it.

Now dmetar() works, but I'll keep it here, just in case.

#' Pool the results of two treatment arms
#'
#' This function allows to pool the mean, standard deviation and sample size of two experimental groups
#' of a study. Results of two treatment arms may be pooled to mitigate the risk of a unit-of-analysis error
#' and to avoid "double-counting" in meta-analyses in which studies with more than two experimental groups
#' are included.
#'
#' @usage pool.groups(n1, n2, m1, m2, sd1, sd2)
#'
#' @param n1 Numeric vector or single number. The number of participants in arm 1.
#' @param n2 Numeric vector or single number. The number of participants in arm 2.
#' @param m1 Numeric vector or single number. The mean in arm 1.
#' @param m2 Numeric vector or single number. The mean in arm 2.
#' @param sd1 Numeric vector or single number. The standard deviation (\eqn{SD}) in arm 1.
#' @param sd2 Numeric vector or single number. The standard deviation (\eqn{SD}) in arm 2.
#'
#' @details Many randomized-controlled trials do not only include a single intervention
#' and control group, but compare the effect of two or more interventions to a control
#' group. It might be tempting in such a scenario to simply include all the comparisons
#' between the intervention groups and control within a study into one meta-analysis.
#' Yet, researchers should abstain from this practice, as this would mean that the
#' control group is used twice for the meta-analysis, thus “double-counting” the
#' participants in the control group. This results in a \strong{unit-of-analysis error}, as
#' the effect sizes are correlated, and thus not independent, but are treated as if they
#' would stem from independent samples.
#'
#' One way to deal with this is to synthesize the results of the intervention arms to
#' obtain one single comparison to the control group. Despite its practical limitations
#' (sometimes, this would mean synthesizing the results from extremely different types
#' of interventions), this procedure does avoid the unit-of-analysis error problem.
#'
#' To synthesize the pooled effect size data (pooled mean, standard deviation and \eqn{N}), the
#' following formulae are used:
#'
#'\deqn{N_{pooled}=N_1+N_2}
#'\deqn{M_{pooled}=\frac{N_1M_1+N_2M_2}{N_1+N_2}}
#'\deqn{SD_{pooled} = \sqrt{\frac{(N_1-1)SD^{2}_{1}+ (N_2-1)SD^{2}_{2}+\frac{N_1N_2}{N_1+N_2}(M^{2}_1+M^{2}_2-2M_1M_2)} {N_1+N_2-1}}}
#'
#' \strong{What should I do when a study has more than two intervention groups?}
#'
#' If a study has more than two intervention groups you want to synthesize
#' (e.g. four arms, with three distinct intervention arms), you can pool the effect
#' size data for the first two interventions, and then synthesize the pooled data you
#' calculated with the data from the third group.
#'
#' @references Harrer, M., Cuijpers, P., Furukawa, T.A, & Ebert, D. D. (2019).
#' \emph{Doing Meta-Analysis in R: A Hands-on Guide}. DOI: 10.5281/zenodo.2551803. \href{https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/i.html}{Chapter 13.9}
#'
#' @author Mathias Harrer & David Daniel Ebert
#'
#' @return Returns a \code{data.frame} containing the following columns:
#' \itemize{
#' \item \code{Mpooled}: The pooled mean of both groups
#' \item \code{SDpooled}: The pooled standard deviation of both groups
#' \item \code{Npooled}: The pooled number of participants of both groups
#' }
#'
#' @export
#'
#' @seealso \code{\link{se.from.p}}
#'
#' @examples
#' pool.groups(n1 = 50, n2 = 56,
#'     m1 = 7.83, m2 = 8.32,
#'     sd1 = 3.52, sd2 = 2.25)



pool.groups = function(n1, n2, m1, m2, sd1, sd2) {

    n1 = n1
    n2 = n2
    m1 = m1
    m2 = m2
    sd1 = sd1
    sd2 = sd2

    if (is.numeric(n1) == FALSE) {
        stop("'n1' must by of type numeric().")
    }

    if (is.numeric(n2) == FALSE) {
        stop("'n2' must by of type numeric().")
    }

    if (n1 < 1 | n2 < 1) {
        stop("'n1' and 'n2' must both the greater than 0.")
    }

    if (is.numeric(m1) == FALSE) {
        stop("'m1' must by of type numeric().")
    }

    if (is.numeric(m2) == FALSE) {
        stop("'m2' must by of type numeric().")
    }

    if (is.numeric(sd1) == FALSE) {
        stop("'sd1' must by of type numeric().")
    }

    if (is.numeric(sd2) == FALSE) {
        stop("'sd2' must by of type numeric().")
    }

    Npooled = n1 + n2
    Mpooled = (n1 * m1 + n2 * m2)/(n1 + n2)
    SDpooled = sqrt(((n1 - 1) * sd1^2 + (n2 - 1) * sd2^2 + (((n1 * n2)/(n1 + n2)) * (m1^2 + m2^2 - 2 * m1 *
        m2)))/(n1 + n2 - 1))

    return(data.frame(Mpooled, SDpooled, Npooled))
}
 
