---
title: "Butler et al., 2009"
output: html_notebook
---

# Effect size

## Gathering information:

Participants:
1) Schizophrenia n = 20 
n = 17 with schizophrenia
n = 3 with schizoaffective disorder

2)  Control n = 17


Contrast sensitivity (p4-5, experiment 1)
1) Significant main effects of Group
F(1,35) = 7.0 , p = 0.01

2)  Significant main effects of SF
F(2,34) = 515.5 , p \< 0.001

3)  Significant Group x SF interaction
F(2,34) = 4.1 , p = 0.03
Post-hoc analysis of the interaction
3A) Significant 0.5 cycle/degree
t = 3.0 , df = 35 , p = 0.005
3B) 7 cycle/degree (not significant)
t = 0.6 , df = 35 , p = 0.6
3C) 21 cycle/degree (not significant)
t = 1.0 , df = 35 , p = 0.3

## Calculate effect size:

use the F-statistic (see bookdown.org)

1)  Significant main effects of Group (2 groups)
F(1,35) = 7.0 , p = 0.01
```{r}
butler_2009_es <- esc_f(f = 7.0,      # F value of the one-way anova
      grp1n = 20,   # sample size of group 1 
      grp2n = 17,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD
butler_2009_es
```

Post-hoc analysis of the Group X SF interaction
3A) Significant 0.5 cycle/degree
t = 3.0 , df = 35 , p = 0.005
```{r}
butler_2009_es_t <- esc_t(t = 3.0, # t-statistic
      grp1n = 20,
      grp2n = 17,
      es.type = "g")
butler_2009_es_t
```


Scrapping data from Figure 2 (plotdigitizer)
Only mean is possible to get, error bars are not defined.


## Summarizing table

```{r}
butler_2009 <- tibble( es = butler_2009_es_t$es, se = butler_2009_es_t$se ) 

butler_2009$study <- "Butler et al. 2009"
butler_2009$method <- "up-and-down transformed response"  
butler_2009$medication <- "medicated" #n=20 medicated
butler_2009$cpz <- 1195.3 
butler_2009$task <- "2AFC" #2AFC mentioned in the article
butler_2009$SF <- "0.5, 7.0, 21.0"
butler_2009$size <- "5.7 x 5.7" 
butler_2009$BPRS <- 45.5
butler_2009$motion <- FALSE 
butler_2009$duration <- 0.032 
butler_2009$location <- 0
butler_2009$lapses <- FALSE
butler_2009$calculation_statistic <- "t-statistic"  
butler_2009$calculation_data <- "reported" 
butler_2009$calculation_certainty <- "unsure" #scale is "sure", "unsure", "very unsure"

butler_2009
```

## Side note 1
Not sure whether I should use the f-statistic or the t-statistic. The t-statistic is specifically looking at SF = 0.5, whereas the f-statistic looks at the groups over all SF.

