---
title: "Butler et al., 2009"
output: html_notebook
---

# Effect size

## Gathering information:

Participants: 1) Schizophrenia n = 20 -\> n = 17 with schizophrenia -\> n = 3 with schizoaffective disorder

2)  Control n = 17

Contrast sensitivity (p4-5, experiment 1) 1) Significant main effects of Group F(1,35) = 7.0 , p = 0.01

2)  Significant main effects of SF F(2,34) = 515.5 , p \< 0.001

3)  Significant Group x SF interaction F(2,34) = 4.1 , p = 0.03 -\> Post-hoc analysis of the interaction 3A) Significant 0.5 cycle/degree t = 3.0 , df = 35 , p = 0.005

    3B) 7 cycle/degree (not significant) t = 0.6 , df = 35 , p = 0.6

    3C) 21 cycle/degree (not significant) t = 1.0 , df = 35 , p = 0.3

## Calculate effect size:

use the F-statistic (see bookdown.org)

1)  Significant main effects of Group F(1,35) = 7.0 , p = 0.01

```{r}
library(esc)
esc_f(f = 7.0,      # F value of the one-way anova
      grp1n = 20,   # sample size of group 1 
      grp2n = 17,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD

```

2)  Significant main effects of SF F(2,34) = 515.5 , p \< 0.001

```{r}
library(esc)
esc_f(f = 515.5,      # F value of the one-way anova
      grp1n = 20,   # sample size of group 1 
      grp2n = 17,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD

```

3)  Significant Group x SF interaction F(2,34) = 4.1 , p = 0.03

```{r}
library(esc)
esc_f(f = 4.1,      # F value of the one-way anova
      grp1n = 20,   # sample size of group 1 
      grp2n = 17,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD

```

-\> Post-hoc analysis of the interaction 3A) Significant 0.5 cycle/degree t = 3.0 , df = 35 , p = 0.005

```{r}
library(esc)
esc_t(t = 3.0, # t-statistic
      grp1n = 20, # sample size 1
      grp2n = 17, # sample size 2
      es.type = "g") 
```

-\> Post-hoc analysis of the interaction 3B) 7 cycle/degree (not significant) t = 0.6 , df = 35 , p = 0.6

```{r}
library(esc)
esc_t(t = 0.6, # t-statistic
      grp1n = 20, # sample size 1
      grp2n = 17, # sample size 2
      es.type = "g") 
```

-\> Post-hoc analysis of the interaction 3C) 21 cycle/degree (not significant) t = 1.0 , df = 35 , p = 0.3

```{r}
library(esc)
esc_t(t = 1.0, # t-statistic
      grp1n = 20, # sample size 1
      grp2n = 17, # sample size 2
      es.type = "g") 
```
