---
title: "Kéri et al., 2010"
output: html_notebook
---

# Effect size

## Gathering information:

Participants: 1) Schizophrenia n = 20

2)  Control n = 20

Contrast sensitivity (p6, experiment 1) 1) Significant main effects of Group F(1,38) = 6.12 , p \< 0.05 eta-squared = 0.14 ; power = 0.67 Eta-squared is a measure of effect size for use in ANOVA (source: <https://en.wikiversity.org/wiki/Eta-squared>) (can we use this as the effect size?)

2)  Significant main effects of contrast sensitivity type (steady vs pulsed pedestal for M vs P pathways, respectively) F(1,38) = 96.79 , p \< 0.0001 eta-squared = 0.72 ; power = 1.0

3)  Significant main effects of SF (spatial frequency) F(4,152) = 25.15 , p \< 0.0001 eta-squared = 0.40 ; power = 1.0

4)  Significant group x contrast sensitivity type interaction F(1,38) = 17.74 , p \< 0.001 eta-squared = 0.32 ; power = 0.98

5)  Significant Group x SF interaction F(4,152) = 2.65 , p \< 0.05 eta-squared = 0.07 ; power = 0.73

6)  Significant SF x Contrast sensitivity type interaction F(4,152) = 65.57 , p \< 0.0001 eta-squared = 0.63 ; power = 1.0

7)  Significant Groups x contrast sensitivity type x SF interaction F(4,152) = 4.08 , p \< 0.05 eta-squared = 1.0 ; power = 0.91

8)  Significant scz vs control in steady pedestal for M-pathways F(1,38) = 14.27 , p \< 0.001 -\> Tukey's HSD at 0.25 c/d: p \< 0.001 at 0.5 c/d: p \< 0.01

9)  Scz vs control in pulsed pedestal for P-pathways (not significant) p \> 0.1

## Calculate effect size:

use the F-statistic (see bookdown.org)

1)  Significant main effects of Group F(1,38) = 6.12 , p \< 0.05 eta-squared = 0.14 ; power = 0.67

```{r}
library(esc)
esc_f(f = 6.12,      # F value of the one-way anova
      grp1n = 20,   # sample size of group 1 
      grp2n = 20,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD

```

2)  Significant main effects of contrast sensitivity type (steady vs pulsed pedestal for M vs P pathways, respectively) F(1,38) = 96.79 , p \< 0.0001 eta-squared = 0.72 ; power = 1.0

```{r}
library(esc)
esc_f(f = 96.79,      # F value of the one-way anova
      grp1n = 20,   # sample size of group 1 
      grp2n = 20,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD

```

3)  Significant main effects of SF (spatial frequency) F(4,152) = 25.15 , p \< 0.0001 eta-squared = 0.40 ; power = 1.0

```{r}
library(esc)
esc_f(f = 25.15,      # F value of the one-way anova
      grp1n = 20,   # sample size of group 1 
      grp2n = 20,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD

```

4)  Significant group x contrast sensitivity type interaction F(1,38) = 17.74 , p \< 0.001 eta-squared = 0.32 ; power = 0.98

```{r}
library(esc)
esc_f(f = 17.74,      # F value of the one-way anova
      grp1n = 20,   # sample size of group 1 
      grp2n = 20,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD
 
```

5)  Significant Group x SF interaction F(4,152) = 2.65 , p \< 0.05 eta-squared = 0.07 ; power = 0.73

```{r}
library(esc)
esc_f(f = 2.65,      # F value of the one-way anova
      grp1n = 20,   # sample size of group 1 
      grp2n = 20,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD
 
```

6)  Significant SF x Contrast sensitivity type interaction F(4,152) = 65.57 , p \< 0.0001 eta-squared = 0.63 ; power = 1.0

```{r}
library(esc)
esc_f(f = 65.57,      # F value of the one-way anova
      grp1n = 20,   # sample size of group 1 
      grp2n = 20,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD

```

7)  Significant Groups x contrast sensitivity type x SF interaction F(4,152) = 4.08 , p \< 0.05 eta-squared = 1.0 ; power = 0.91

```{r}
library(esc)
esc_f(f = 4.08,      # F value of the one-way anova
      grp1n = 20,   # sample size of group 1 
      grp2n = 20,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD

```

8)  Significant scz vs control in steady pedestal for M-pathways F(1,38) = 14.27 , p \< 0.001 -\> Tukey's HSD at 0.25 c/d: p \< 0.001 at 0.5 c/d: p \< 0.01

```{r}
library(esc)
esc_f(f = 14.27,      # F value of the one-way anova
      grp1n = 20,   # sample size of group 1 
      grp2n = 20,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD

```

9)  Scz vs control in pulsed pedestal for P-pathways (not significant) p \> 0.1

## Side note 1

Effect size calculated from F statistic and eta-squared are not alike? Is this due to a different way of calculation, or a mistake from me?
