---
title: "Dias et al., 2011"
output: html_notebook
---

# Effect size

## Gathering information:

Participants: 1) Schizophrenia n = 27 -\> n = 20 Subgroup (same characteristics) for contrast sensitivity

2)  Control n = 15 -\> n = 9 Subgroup (same characteristics) for contrast sensitivity

Contrast sensitivity (p6) 1) Significant main effects of Group F(1,27) = 11.3 , p = 0.002

2)  Significant Group x SF interaction F(2,26) = 5.49 , p = 0.01

3)  Low SF (0.5c/deg) vs controls (significantly reduced contrast) F(1,27) = 10.7 , p = 0.003

4)  Medium SF (7c/deg) vs controls (not significantly reduced contrast) F(1,27) = 2.28 , p = 0.14

5)  High SF (21c/deg) vs controls (not significantly reduced contrast) F(1,27) = 2.08 , p = 0.16

## Calculate effect size:

use the F-statistic (see bookdown.org)

1)  Significant main effects of Group F(1,27) = 11.3 , p = 0.002

```{r}
library(esc)
esc_f(f = 11.3,      # F value of the one-way anova
      grp1n = 20,   # sample size of group 1 
      grp2n = 9,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD

```

2)  Significant Group x SF interaction F(2,26) = 5.49 , p = 0.01

```{r}
library(esc)
esc_f(f = 5.49,      # F value of the one-way anova
      grp1n = 20,   # sample size of group 1 
      grp2n = 9,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD

```

3)  Low SF (0.5c/deg) vs controls (significantly reduced contrast) F(1,27) = 10.7 , p = 0.003

```{r}
library(esc)
esc_f(f = 10.7,      # F value of the one-way anova
      grp1n = 20,   # sample size of group 1 
      grp2n = 9,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD

```

4)  Medium SF (7c/deg) vs controls (not significantly reduced contrast) F(1,27) = 2.28 , p = 0.14

```{r}
library(esc)
esc_f(f = 2.28,      # F value of the one-way anova
      grp1n = 20,   # sample size of group 1 
      grp2n = 9,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD
 
```

5)  High SF (21c/deg) vs controls (not significantly reduced contrast) F(1,27) = 2.08 , p = 0.16

```{r}
library(esc)
esc_f(f = 2.08,      # F value of the one-way anova
      grp1n = 20,   # sample size of group 1 
      grp2n = 9,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD
 
```
