---
title: "Cadenhead et al., 2013"
output: html_notebook
---

# Effect size

## Gathering information:

Participants:
1) Schizophrenia n = 53
7 excluded for the contrast sensitivity: n = 46

2)  Control n = 53

3)  Schizotypical personality disorder (SPD) n = 22
1 excluded for the contrast sensitivity: n = 21

Contrast sensitivity (p4)
1) Significant main effects of Group
F(2,118) = 8.81 , p \< 0.001
post-hoc t-test:
Control vs SPD: p \< 0.05 (significant)
Control vs Scz: p \< 0.001 (significant)
SPD vs Scz: not significant

2)  Group x stimulus condition interaction (not significant)
F(2,117) = 0.56 , NS

## Calculate effect size:

use the F-statistic (see bookdown.org)

1)  Significant main effects of Group (3 groups)
F(2,118) = 8.81 , p \< 0.001

```{r}
cadenhead_2013_es <- esc_f(f = 8.81,      # F value of the one-way anova
      grp1n = 46,   # sample size of group 1 
      grp2n = 21,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD
cadenhead_2013_es
```


## Summarizing table

```{r}
cadenhead_2013 <- tibble( es = cadenhead_2013_es$es, se = cadenhead_2013_es$se ) 
cadenhead_2013

cadenhead_2013$study <- "Cadenhead et al. 2013"
cadenhead_2013$method <- "luminance modulation" # adaptative, mc, ... 
cadenhead_2013$medication <- TRUE #n=48 medicated, n=5 unmedicated
cadenhead_2013$cpz <- "NA"  #in mg
cadenhead_2013$task <- "2AFC" 
cadenhead_2013$SF <- 1.22
cadenhead_2013$BPRS <- NA
cadenhead_2013$motion <- TRUE #is grating moving?
cadenhead_2013$duration <- 0.12 #Duration of the stimulus in seconds
cadenhead_2013$location <- 0 #Where the stimulus was presented in degrees of visual angle (fixation = 0)
cadenhead_2013$lapses <- "?"  #In lapses, we can include whether they control for lapses (TRUE) or not (FALSE).
cadenhead_2013$calculation_statistic <- "f test"  #"t-test", "m and sd"
cadenhead_2013$calculation_data <- "reported" #"scrapping", "reported", "raw"
cadenhead_2013$calculation_certainty <- "very unsure" #scale is "sure", "unsure", "very unsure"

cadenhead_2013
```

## Side note 1

I believe the es is wrong, since the effect of group was measured for the three groups, and not only for ctrl vs scz.

## Side note 2

I think information could be gotten from the figures. However, I am not sure which figure is the correct one. (I think figure 1)

I think information could be gotten from the figures. However, I am not sure which figure is the correct one. (I think figure 1). I don't know if we need to look at luminance of chromatic condition. Not sure how to do this.
