---
title: "Caldarone et al., 2013"
output: html_notebook
---

# Effect size

## Gathering information:

Participants:
1) Schizophrenia n = 15

2)  Control n = 15


Contrast sensitivity (p4)
1) Significant main effects of Group
F(1,56) = 11.769 , p \< 0.005

2)  Significant Group x Condition interaction
F(1,56) = 4.632 , p \< 0.05


Contrast sensitivity in fMRI (p5)
3) SF = 0.5 at 32ms:
Controls: mean = 54.69 , sd = 17.03
Scz: mean = 50.70 , sd = 19.15

4) SF = 4 at 500 ms:
Controls: mean = 41.43 , sd = 24.17
Scz: mean = 23.52 , sd = 21.68


## Calculate effect size:
use the F-statistic (see bookdown.org)

###  Significant main effects of Group (2 groups)
F(1,56) = 11.769 , p \< 0.005
```{r}
caldarone_2013_es_f <- esc_f(f = 11.769,      # F value of the one-way anova
      grp1n = 15,   # sample size of group 1 
      grp2n = 15,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD
caldarone_2013_es_f
```

See Figure 3 for mean contrast sensitivity - problem: scale of y-axis is wrong, plotdigitizer cannot compute data.


### FMRI results
3) SF = 0.5 at 32ms:
Controls: mean = 54.69 , sd = 17.03
Scz: mean = 50.70 , sd = 19.15
```{r}
caldarone_2013_es_sf0.5 <- esc_mean_sd(grp1m = 54.69, grp2m = 50.70,  # group mean
            grp1sd = 17.03, grp2sd = 19.15, # group sd
            grp1n = 15, grp2n = 15, 
            es.type = "g")
caldarone_2013_es_sf0.5
```


## Summarizing table

```{r}
caldarone_2013 <- tibble(es = caldarone_2013_es_f$es, se = caldarone_2013_es_f$se ) 

caldarone_2013$study <- "Caldarone et al. 2013"
caldarone_2013$method <- "up-down transform rule" #UDTR
caldarone_2013$medication <- "medicated" #n=15 medicated
caldarone_2013$cpz <- 783.33
caldarone_2013$task <- "2AFC" #2AFC mentioned in the article
caldarone_2013$SF <- "0.5, 4"
caldarone_2013$size <- "6 x 6" 
caldarone_2013$BPRS <- NA
caldarone_2013$motion <- FALSE 
caldarone_2013$duration <- "0.032 for SF=0.5, 0.5 for SF=4" 
caldarone_2013$location <- NA
caldarone_2013$lapses <- FALSE 
caldarone_2013$calculation_statistic <- "f-statistic"  
caldarone_2013$calculation_data <- "reported" 
caldarone_2013$calculation_certainty <- "unsure" #scale is "sure", "unsure", "very unsure"

caldarone_2013
```


## Side note 1
This study also measured contrast sensitivity with fMRI. I am not sure how to interpret these results. Do I also use them to caculate the effect size?
