---
title: "Caldarone et al., 2013"
output: html_notebook
---

# Effect size

## Gathering information:

Participants: 1) Schizophrenia n = 15

2)  Control n = 15

Contrast sensitivity (p4) 1) Significant main effects of Group F(1,56) = 11.769 , p \< 0.005

2)  Significant Group x Condition interaction F(1,56) = 4.632 , p \< 0.05

Contrast sensitivity in fMRI (p5) 3) 0.5c/deg at 32ms:(M +- SD) Controls: 54.69 +- 17.03 Scz: 50.70 +- 19.15

4)  4c/deg at 500 ms: (M +- SD) Controls: 41.43 +- 24.17 Scz: 23.52 +- 21.68

## Calculate effect size:

use the F-statistic (see bookdown.org)

1)  Significant main effects of Group F(1,56) = 11.769 , p \< 0.005

```{r}
library(esc)
esc_f(f = 11.769,      # F value of the one-way anova
      grp1n = 15,   # sample size of group 1 
      grp2n = 15,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD

```

2)  Significant Group x Condition interaction F(1,56) = 4.632 , p \< 0.05

```{r}
library(esc)
esc_f(f = 4.632,    # F value of the one-way anova
      grp1n = 15,   # sample size of group 1 
      grp2n = 15,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD

```

3)  0.5c/deg at 32ms:(M +- SD) Controls: 54.69 +- 17.03 Scz: 50.70 +- 19.15

```{r}
library(esc)
esc_mean_sd(grp1m = 54.69, grp2m = 50.70,  # group mean
            grp1sd = 17.03, grp2sd = 19.15, # group sd
            grp1n = 15, grp2n = 15, 
            es.type = "g")
```

4)  4c/deg at 500 ms: (M +- SD) Controls: 41.43 +- 24.17 Scz: 23.52 +- 21.68

```{r}
library(esc)
esc_mean_sd(grp1m = 41.43, grp2m = 23.52,  # group mean
            grp1sd = 24.17 , grp2sd = 21.68, # group sd
            grp1n = 15, grp2n = 15, 
            es.type = "g")
```

## Side note 1

This study also measured contrast sensitivity with fMRI. I am not sure how to interpret these results. Do I also use them to caculate the effect size?
