---
title: "Cimmer et al., 2006"
output: html_notebook
---

# Effect size

## Gathering information:

Participants:
1) Schizophrenia n = 44
n = 32 with non-deficit schizophrenia
n = 12 with deficit schizophrenia

2)  Control n = 20

Contrast sensitivity (p3)
1) Significant main effects of Group (deficit + non-deficit + controls)
F(2,61) = 14.62 , p \< 0.0001

Tukey's HSD test
p \< 0.001 (schizophrenia vs controls)
p = 0.17 (non-deficit vs deficit)

## Calculate effect size:
use the F-statistic (see bookdown.org)

### Significant main effects of Group (3 groups)
F(2,61) = 14.62 , p \< 0.0001 
```{r}
# F-statistic: 3 groups, thus not applicable
```


### Scrapping data from figure 2 (use plotdigitizer)
Non-deficit (n=32): mean = 2.2919685074449494, 95%CI = (2.2390551065646807 - 2.3411023518852456)
Deficit (n=12): mean = 2.200314934201157, 95%CI = (2.11622047383731 - 2.2834645703349024) 
Controls (n=20): mean = 2.4629921171292537, 95%CI = (2.3996850441722124 - 2.5262992117129253)



DL. WE DON'T KNOW IF THEY USE Z OR T TO CALCULATE CI, BUT GIVEN THAT T IS MORE CORRECT, LET'S ASSUME THEY USED THIS ONE. USING Z OR T DOES NOT MAKE A BIG CHANGE

```{r}
# Function to calculate SD from mean, n, and CI
calculate_sd <- function(mean, n, ci_lower, ci_upper) {
  # Calculate the z-score for the desired confidence level (e.g., 95%)
  t_statistic <- qt(1 - (1 - 0.95) / 2, df = n)

  # Calculate the standard deviation
  sd <- (ci_upper - ci_lower) / (2 * t_statistic / sqrt(n))
  
  return(sd)
}
```
### Calculate sd per group

DL. IT IS BETTER NOT TO USE VARIABLE NAMES SUCH "mean" BECAUSE IT IS EASY TO MAKE ERRORS IF THIS VARIABLE APPEARS IN DIFFERENT LOCATIONS WITH DIFFERENT VALUES IN THE CODE. IT IS BETTER mean_non_deficit_cimmer_2006 EVEN IF IT IS VERY LARGE. ANOTHER SOLUTION IS TO USE THIS LONG NAME ONLY FOR nd_sd. FOR EXAMPLE nd_sd_cimmer_2006 and then do something like 

calculate_sd(mean = 2.2919685074449494, 
  n = 32, 
  ci_lower = 2.2390551065646807 ....
  
SO YOU DONT NEED TO NAME  n, ci_lower....

Non-deficit (n=32): mean = 2.2919685074449494, 95%CI = (2.2390551065646807 - 2.3411023518852456)
```{r}
# Non-deficit 

mean <- 2.2919685074449494
n <- 32
ci_lower <- 2.2390551065646807
ci_upper <- 2.3411023518852456

nd_sd <- calculate_sd(mean, n, ci_lower, ci_upper)
print(nd_sd)

```

Deficit (n=12): mean = 2.200314934201157, 95%CI = (2.11622047383731 - 2.2834645703349024)
```{r}
# Deficit 

mean <- 2.200314934201157
n <- 12
ci_lower <- 2.11622047383731
ci_upper <- 2.2834645703349024

d_sd <- calculate_sd(mean, n, ci_lower, ci_upper)
print(d_sd)
```

Controls (n=20): mean = 2.4629921171292537, 95%CI = (2.3996850441722124 - 2.5262992117129253)
```{r}
# Control 

mean <- 2.4629921171292537
n <- 20
ci_lower <- 2.3996850441722124
ci_upper <- 2.5262992117129253

c_sd <- calculate_sd(mean, n, ci_lower, ci_upper)
print(c_sd)
```

### Pool mean and sd of deficit and non-deficit group
Non-deficit (n=32): mean = 2.2919685074449494, 95%CI = (2.2390551065646807 - 2.3411023518852456)
Deficit (n=12): mean = 2.200314934201157, 95%CI = (2.11622047383731 - 2.2834645703349024)
```{r}
sz_pooled <- pool.groups(n1 =32 ,   # sample size group 1
            n2 = 12,   # sample size group 2
            m1 = 2.2919685074449494,  # mean group 1
            m2 = 2.200314934201157,    # mean group 2
            sd1 = nd_sd,   # sd group 1
            sd2 = d_sd) # sd group2 
sz_pooled
```

### Calculate the effect size of control vs sz_pooled
Controls (n=20): mean = 2.4629921171292537,
```{r}
cimmer_2006_es <- esc_mean_sd(grp1m = 2.4629921171292537, grp2m = sz_pooled$Mpooled,  # group mean
            grp1sd = c_sd, grp2sd = sz_pooled$SDpooled, # group sd
            grp1n = 20, grp2n = sz_pooled$Npooled, 
            es.type = "g")
cimmer_2006_es
```


## Summarizing table

DL THE TASK SHOULD BE 2IFC

cimmer_2006$lapses <- TRUE, IT SHOULD BE FALSE BECAUSE THEY DON'T CONTROL FOR LAPSES, RIGHT?  

calculation_certainty SURE

```{r}
cimmer_2006 <- tibble( es = cimmer_2006_es$es, se = cimmer_2006_es$se ) 
cimmer_2006

cimmer_2006$study <- "Cimmer et al. 2006"
cimmer_2006$method <- "adaptive" 
cimmer_2006$medication <- "medicated" #all patients were on medication
cimmer_2006$cpz <- "NA"  #Dose is not mentioned
cimmer_2006$task <- "2AFC" #2AFC means two alternative forced choice
cimmer_2006$SF <- 0.5
cimmer_2006$size <- 13
cimmer_2006$BPRS <- "NA" #not mentioned
cimmer_2006$motion <- TRUE 
cimmer_2006$duration <- 0.5 
cimmer_2006$location <- 0
cimmer_2006$lapses <- "TRUE"  
cimmer_2006$calculation_statistic <- "m and sd"  
cimmer_2006$calculation_data <- "scrapping, calculate sd, pooling" 
cimmer_2006$calculation_certainty <- "unsure" #scale is "sure", "unsure", "very unsure"

cimmer_2006
```

## Side note 1
The F-statistic is 3 groups (deficit, non-deficit and healthy controls), thus not applicable. 

Scrapping data from Figure 2, calculate sd from 95%CI, then pooling deficit and non-deficit groups. Then calculate es from m and sd.

