---
title: "Chen et al., 2003"
output: html_notebook
---

# Effect size

## Gathering information:

Participants:
1) Schizophrenia n = 45
n = 12 with schizophrenia
n = 33 with schizoaffective disorder
also classified according to type of antipsychotic medication

2)  Control n = 39

3)  First-degree relatives n = 24


Contrast sensitivity (p3)
1) Schizophrenia group (as a whole) vs healthy controls (significant)
scz: mean = 0.0036 ; SD = 0.0039
ctrl: mean = 0.0025 ; SD = 0.0016 
t = 2.04, df = 82, p\<0.05
Effect size of group difference: 0.71 (small) (maybe relatives as a group also included, not stated in paper)

2)  Classified schizophrenia patients by type of antipsychotic medication (not neccessary for us)

3)  First degree relatives vs healthy controls (not significant)
rel: mean = 0.0022 ; SD = 0.001
ctrl: mean = 0.0025 ; SD = 0.0016

## Calculate effect size:

use the means, the standards deviations and sample sizes (see tutorials meta-analysis)

1)  Schizophrenia group (as a whole) vs healthy controls
scz: mean = 0.0036 ; SD = 0.0039
ctrl: mean = 0.0025 ; SD = 0.0016

```{r}
chen_2003_es <- esc_mean_sd(grp1m = 0.0036, grp2m = 0.0025, 
            grp1sd = 0.0039, grp2sd = 0.0016, 
            grp1n = 45, grp2n = 39, 
            es.type = "g")
chen_2003_es
```

1)  Schizophrenia group (as a whole) vs healthy controls scz:
t = 2.04, df = 82, p\<0.05
```{r}
chen_2003_t_statistic <- esc_t(t = 2.04,
      grp1n = 45,
      grp2n = 39,
      es.type = "g")
chen_2003_t_statistic
```
DL: IT DOES NOT MUCH THE PREVIOUS CALCULATION, SO I THINK THEY MADE SOMETHING WRONG

3)  First degree relatives vs healthy controls (not significant)
rel: mean = 0.0022 ; SD = 0.001
ctrl: mean = 0.0025 ; SD = 0.0016

```{r}
chen_2003_es_rel <- esc_mean_sd(grp1m = 0.0022, grp2m = 0.001, 
            grp1sd = 0.0039, grp2sd = 0.0016, 
            grp1n = 24, grp2n = 39, 
            es.type = "g")
chen_2003_es_rel
```

## Summarizing table

DL: BECAUSE THEY PRESENT ONE STIMULUS AFTER THE OTHER THIS IS TYPICALLY CALLED 2IFC (TWO INTERVAL FORCED CHOICE)

staircase is an adaptive method

```{r}
chen_2003 <- tibble( es = chen_2003_es$es, se = chen_2003_es$se ) 

chen_2003$study <- "Chen et al. 2003"
chen_2003$method <- "staircase" # adaptative, mc, ... (Do they use a special method to display contrast?) 
chen_2003$medication <- "medicated and unmedicated" #TRUE #n=39 were on medication, n=6 not on medication
chen_2003$cpz <- "NA"  #Dose is not mentioned
chen_2003$task <- "2IFC" #2AFC means two alternative forced choice
chen_2003$SF <- 0.5
chen_2003$size <- 10
chen_2003$BPRS <- 42.4
chen_2003$motion <- TRUE #is grating moving?
chen_2003$duration <- 0.3 #Duration of the stimulus in seconds
chen_2003$location <- 0 #Where the stimulus was presented in degrees of visual angle (fixation = 0)
chen_2003$lapses <- FALSE  #In lapses, we can include whether they control for lapses (TRUE) or not (FALSE).
chen_2003$calculation_statistic <- "m and sd"  #"t-test", "m and sd"
chen_2003$calculation_data <- "reported" #"scrapping", "reported", "raw"
chen_2003$calculation_certainty <- "sure" #scale is "sure", "unsure", "very unsure"

chen_2003
```

## Side note 1

The authors reported an effect size, however, my calculations do not match this effect size. Am I doing something wrong?

DL: I THINK YOUR CALCULATIONS ARE FINE.

## Side note 2

The authors mention that the grating is moving with a temporal frequency of 5 Hz. Does this mean the study is about motion and not solely contrast detection?

DL: IT IS ABOUT DETECTION, IT IS JUST THAT PARTICIPANTS NEED TO DETECT A MOVING GRATING. TWO CIRCLES ARE PRESENTED ONE AFTER THE OTHER AND IN ONE OF THE CIRCLE THE GRATING IS PRESENTED. THE TASK OF THE PARTICIPANT IS TO SAY FIRST OR SECOND (CIRCLE).

## Side note 3

The authors also do contrast sensitivity calculations based on the type on antipsychotic medication. I did not calculate these effect sizes, since I don't believe it is relevant.

DL, YES FOR NOW LESS FOCUS ON POOLING EVERYTHING, THE IDEA OF THE STUDY OF SEPARATING BY MEDICATION IS GREAT, THE PROBLEM WITH THE STUDY IS THAT FOR THE GROUP NO MEDICATION AND TYPICAL ANTIPSYCHOTICS, THEY HAVE VERY FEW PARTICIPANTS. PAPER RELEVANT FOR THE DISCUSSION SECTION IN THE PART ABOUT "COULD IT BE MEDICATION?"
